---
title: "Project 1"
author: "name"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  pdf_document:
  highlight: Null
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(mosaic)
library(openintro)
pew_energy_dataframe <- as.data.frame(pew_energy_2018)

```

## Introduction

 
```{r tally, echo=FALSE, comment=NA}

tally(~coal_mining,data=pew_energy_dataframe)
```


## A bar graph


```{r pew_energy_dataframe, echo=FALSE, comment=NA}
gf_bar(~coal_mining,data=pew_energy_dataframe,xlab = "Would you favor an increase in Coal Mining for energy Production?", title="How do people feel about Coal Mining?")
```

## Making the confidence interval:

### Independence 

### Success failure Condition

### Summary:

To get p-hat notation type $\hat{p}$ 

For the distribution notation type: 
$\hat{p} \sim   N(\hat{p},SE)$

Don't forget to change your $\hat{p}$ and standard error in the distribution notation above, also delete this sentence. Edit this two senteces above so they make sense in a report. 


```{r confint, echo=FALSE, comment=NA}
test_results<-prop.test(~coal_mining,success ="favor_increase",conf.level = 0.90, data= pew_energy_dataframe)

test_results$conf.int
```


## Excercise



## Conclusion

