---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# MTH142Rtutorials

This package is a collection of 14 learnr tutorials I made for an Intro to Statistics Course taught at Holyoke Community College.

I use the `mosaic` , `openintro`, and `tidyverse` packages. Formula \~ syntax is used whenever possible.

The text is OpenIntro's [[Introduction to Statistics]{.underline}.](https://www.openintro.org/book/os/) [MyOpenMath](https://www.myopenmath.com/) is the LMS and has problems from the text.

There is a template course on MyOpenMath that was put together by Adam Gilbert of Southern New Hampshire University. If you'd like to copy my template please contact me via the email link above.


## Installation

You can install the development version of MTH142Rtutorials from [GitHub](https://github.com/) with:

``` r
remotes::install_git("https://github.com/Nics-Github/MTH142Rtutorials")
```


## Example

This is a basic example which shows you how to load the library.

```{r example}
#Load the libraries
library(MTH142Rtutorials)

```

